---
title: "Narrative"
author: "Yi Lu"
date: "12/10/2020"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = F)
```

## Brief background
This project pertains to a brief analysis of US politicians' address on "social
ism". "Socialism" as both an ideology and a practice that criticizes and seeks to
overcome capitalist market economy has aroused considerable attack and negation
from the mainstream politicians. Neither Democrats nor Republicans would publicly
support socialism, but their concepts on and patterns of using the term "socialism"/"socialist" differed. Based on public documents retrieved
from UCSB's American Presidency Project, this project attempts to show the diff-
erent patterns of use of "socialism" as a politically sensitive term. I use  
plotting and wordcloud analysis to explore the data.

## Collecting data

Getting data can be very painful especially when many of the raw materials are
irregular in their formats and you cannot write a one-time-for-all code to retr-
ieve them. In this project I use data scraped from the American Presidency 
Project by searching the keyword "socialism"

```{r}
# Getting necessary urls from the searching pages is what we want, but first we
# need to prepare R packages and the searching pages.

library(tidyverse)
library(rvest)
library(stringr)
library(purrr)
library(lubridate)
library(tm)
library(wordcloud)

# These are the results by searching keyword "socialism". I compile them into a vector. 
no_socialism <- c(
"https://www.presidency.ucsb.edu/advanced-search?field-keywords=%22socialism%22&field-keywords2=&field-keywords3=&from%5Bdate%5D=&to%5Bdate%5D=&person2=&items_per_page=100", 
"https://www.presidency.ucsb.edu/advanced-search?field-keywords=%22socialism%22&field-keywords2=&field-keywords3=&from%5Bdate%5D=&to%5Bdate%5D=&person2=&items_per_page=100&page=1", 
"https://www.presidency.ucsb.edu/advanced-search?field-keywords=%22socialism%22&field-keywords2=&field-keywords3=&from%5Bdate%5D=&to%5Bdate%5D=&person2=&items_per_page=100&page=2", 
"https://www.presidency.ucsb.edu/advanced-search?field-keywords=%22socialism%22&field-keywords2=&field-keywords3=&from%5Bdate%5D=&to%5Bdate%5D=&person2=&items_per_page=100&page=3",
"https://www.presidency.ucsb.edu/advanced-search?field-keywords=%22socialism%22&field-keywords2=&field-keywords3=&from%5Bdate%5D=&to%5Bdate%5D=&person2=&items_per_page=100&page=4",
"https://www.presidency.ucsb.edu/advanced-search?field-keywords=%22socialism%22&field-keywords2=&field-keywords3=&from%5Bdate%5D=&to%5Bdate%5D=&person2=&items_per_page=100&page=5")

# Write the csv of those unprocessed urls.
write.csv(no_socialism, "~/links.csv")
```


```{r}
# Create a scraping function to retrieve the urls we need (those with public remarks content).
stronk <- function(url){
  yes <- read_html(url)

  yes1 <- yes %>%  
  html_nodes("a") %>% 
  html_attr("href") 

yes2 <- yes1[str_starts(yes1, "/documents")] 
yes3 <- paste0("https://www.presidency.ucsb.edu", yes2)[-(1:4)] 
  return(yes3)
}

```


```{r}
# Unfortunately those document pages do not contain the information about Presidents' political parties. Therefore we need to separately scrape some other urls in which you can find presidents' parties.

party <- function(url){
  coup <- read_html(url)

  coup1 <- coup %>%  
  html_nodes("a") %>% 
  html_attr("href")

  coup2 <- coup1[str_starts(coup1, "/people")] 

  coup3 <- paste0("https://www.presidency.ucsb.edu", coup2)[-1]
}


```

## Processing data
This process is in fact not strikingly different from the previous one because now I am scraping the text information from those urls prepared in the previous step. Nevertheless we are going to process the raw urls to retrieve more useful information.

```{r}
# Create the scraping functions to retrieve the information we need from the pages.

scrape_docs <- function(URL){
  doc <- read_html(URL)

  speaker <- html_nodes(doc, ".diet-title a") %>% 
    html_text()
  
  date <- html_nodes(doc, ".date-display-single") %>%
    html_text() %>%
    mdy()
  
  text <- html_nodes(doc, "div.field-docs-content") %>%
    html_text()
  
  all_info <- list(speaker = speaker, date = date, text = text)
  
  return(all_info) 
  # This returns the content of public remarks that have mentioned "socialism".
}

# Scraping from people's info pages.
obtain <- function(url){
  page <- read_html(url)
  
  party <- html_nodes(page, ".f-item") %>%
    html_text()
  
  get <- list(party = party[4])
  
  return(get)
  # This returns the political parties the POTUS affiliated with.
}

```


```{r}
# Map the scraping function onto the vector we created.
maga <- map(no_socialism, stronk) 
                                  
maga <- unlist(maga) 

potus_stronk <- map_dfr(maga, scrape_docs)

potus_party <- map(no_socialism, party)

potus_party <- unlist(potus_party)

party_name <- map_dfr(potus_party, obtain)

new_potus <- data.frame(party_name, potus_stronk)

# Write the csv file of the processed data.
write.csv(new_potus, "~/potus.csv", row.names = F)
```

## Analysis and Visualization
Now the raw data is processed, we are ready to analyze it with special tools of
visualization.

```{r eval=FALSE}
# We'd like to see how many of public remarks related to "socialism" had been made from the period amid global financial crisis. So we set the date at the very beginning of 2008.
num <- new_potus %>%
  count(date > "2008-1-30")
pie(num$n, labels = num$`date > "2008-1-30"`, clockwise = T, main = "Public remarks after 2008")

# For comparison, we would like to see how many public remarks were made before Cold War formally ended (1991.12.25 when Gorbachev resigned from his post).
num1 <- new_potus %>%
  count(date < "1991-12-27")
pie(num1$n, labels = num1$`date < "1991-12-27"`, clockwise = T, main = "Public remarks before 1991")
# Discussion of "socialism" among politicians is much more frequent after 2008, as the data shows that the public remarks made after 2008 take more than a half of all documents. This reminds us that how concepts related to socialism obtained popular attention after a severe crisis of the capitalist market economy.
```


```{r eval=FALSE}
# We now want to see the 10 politicians who talked most about "socialism"
num_speaker <- new_potus %>%
  count(speaker) %>%
  slice_max(n, n=10)
view(num_speaker)
# Guess who talks the most about "socialism"? Donald J. Trump! By October 2020 he had referred to "socialism" and "socialist" in 127 public remarks. This is one time more than Truman's 51 remarks which stand at the second place.  

# Using ggplot() to visualize the results 
ggplot(data = num_speaker, aes(x = reorder(speaker, n), y = n)) + geom_bar(stat = "identity") + theme(axis.text.x = element_text(
angle = 45, size = 9, hjust = 1))+xlab("Speakers")+ylab("Number of docs")+
  ggtitle("10 speakers who talked the most about socialism")

## If we know nothing about politicians at all, we would think that Trump really "loves" socialism! 
```


```{r eval=FALSE}
# We want to see with and without Trump, how Republicans' frequency of talking publicly about socialism changes.
num2 <- new_potus %>%
  count(party == "Republican")
pie(num2$n, labels = num2$`party == "Republican"`, clockwise = T, main = "Public remarks made by GOP Presidents")
# With Trump included, Republican Presidents made public comments on socialism as frequently as their Democratic counterparts. 

num3 <- new_potus %>%
  filter(!(speaker == "Donald J. Trump")) %>%
  count(party == "Republican")
pie(num3$n, labels = num3$`party == "Republican"`, clockwise = T, main = "Public remarks made by GOP Presidents/without Trump")
# With Trump excluded, however, Republicans' proportion significantly decreased.
```


```{r eval=FALSE}
# Now we turn to analyze the words those speakers used alongside their mentioning of socialism. We need to write a function so that I can get the word cloud from the politicians as soon as I enter their names.

wordcount <- function(speakers){
# This step gives texts' paragraphs in which speakers directly mentioned "socialism".
  address <- new_potus %>%
  filter(speaker == speakers) %>%
  select(text) %>%
  unlist() %>%
  str_split("\n")
address <- unlist(address)
on_soc <- address[str_detect(address, "socialis")]

# This step produces wordclouds for those paragraphs related to "socialism".
on_soc <- Corpus(VectorSource(on_soc))
on_soc <- DocumentTermMatrix(on_soc,
                            control = list(stopwords = TRUE,
                          tolower = TRUE,
                          removeNumbers = TRUE,
                          removePunctuation = TRUE))
freq <- colSums(as.matrix(on_soc))
sums <- as.data.frame(freq)
sums <- rownames_to_column(sums)
colnames(sums) <- c("term", "count")
sums <- arrange(sums, desc(count))
head <- sums[1:75,]
fin <- wordcloud::wordcloud(words = head$term, freq = head$count,
                     min.freq = 1000,
  max.words=100, random.order=FALSE, rot.per = 0.3)

return(fin)}

# We will first examine Trump's wordcloud.
wordcount("Donald J. Trump")

# Entering Trump's name and we found that "democrats" has been mentioned a lot alongside his comment on socialism. This should not be surprising because it is known that Trump has relentlessly attacked democrats by labeling them as "socialist" or even "far left". In addition, Trump has also mentioned a lot about Venezuela and Cuba, which are often being used by conservatives as examples of socialist failures to rebuke left-wing policies. 
# Trump also mentioned "communism" when talking about socialism. This is also a common rhetoric among conservatives to infer that democrats' policies have commonality with communist radical ideas.
# Another interesting note is the presence of word "booing" as a description of audience's reaction towards Trumps' mention of "socialism". 

wordcount("Barack Obama")

# Entering Obama's name and we found that "tax", "security", "government" are very frequently mentioned alongside "socialism". This reflects the themes of policy debates during Obama's presidential campaign and his administration, and indicates how Obama's policies on tax and social security had been criticized by conservatives as "socialist".  

# We also compare the wordclouds with those of Reagan and Carter. Noticeably, Carter also mentioned quite a lot about "security" like Obama did. Carter also mentioned "republicans" frequently alongside "socialism", implying that conservatives' accusation of Democrats' socialist inclination has a long tradition. And because of the background of Cold War both Reagan and Carter talked about "communism" quite frequently. 
wordcount("Ronald Reagan")
wordcount("Jimmy Carter")

```

## Future Work
As I have said in the beginning, this analysis is generally brief. Due to the technical limits this analysis does not provide a detailed analysis of the contexts of politicians' reference to socialism. In general, though, socialism is still a tabooed word for mainstream politicians and most of them deny any associations with the concepts and practices related to that. I hope in the future there could be more precise text analysis on politicians' ideology patterns across time.   
